### 2016-05-24 intro.tex
hacking together an intro

>>>>

Bloom filters have a broad range of practical applications, for example, in content-distribution networks, large database query processing, routing algorithms for peer-to-peer networks, protocols for establishing linkages between medical-record databases, fair routing of TCP packets, Bitcoin wallet synchonization. \tsnote{need citations}  Given that NY is addressing such a useful real-world object, we find their formalism, both the syntax and security notions, to be less precise and useful than one would want.  Let us explain.

 Syntactically, NY says a Bloom filter (with a steady representation) is a pair of algorithms $\mathbf{B}=(\mathbf{B}_1, \mathbf{B}_2)$.  The setup algorithm~$\mathbf{B}_1$ is randomized, and on input a set~$\mathcal{S}$ it returns a representation~$M$ (from some undefined, implicit set of representations).  The query algorithm~$\mathcal{B}_2$ is determinisic, and on input a representation~$M$ and an element~$x \in \mathcal{U}$, it returns a bit.  For correctness they make the classical demand, that for all $x \in \mathcal{S}$ we have $\Prob{\mathbf{B}_2(\mathbf{B}_1(S),x)=1}=1$.  For soundness, adversary~$A$ plays the following game, ``Adversarial-resilient Bloom Filter with a steady representation''.  First, $M \getsr \mathbf{B}_1(\mathcal{S})$.  Then the adversary is given the set~$\mathcal{S}$ and may make queries $x_1,x_2,\ldots,x_q$ to an oracle for $\mathbf{B}_2(M,\cdot)$.  At the end of its execution, the adversary outputs~$x^*$ and wins the game if (1) $x^* \not\in \mathcal{S} \cup \{x_1,x_2,\ldots,x_q\}$, and (2) $\mathbf{B}_2(M,x^*)=1$.

First, we note that the security notion forbids~$A$ to win if it outputs $x^* \in \{x_1,x_2,\ldots,x_q\}$, even if one of these was a false-positive.  
%
Second, we note that the NY syntax does not capture the size of~$M$ as a parameter; the surrounding text does say that $\mathbf{B}_1$ ``outputs a compressed representation [of $\mathcal{S}$] $\mathbf{B}_1(\mathcal{S})=M$'' but what exactly this means is never addressed.  The formal syntax admits $\mathbf{B}_1(\mathcal{S})=\mathcal{S}$ and $\mathbf{B}_2(\mathcal{S},x)=1 \Leftrightarrow x \in \mathcal{S}$, which is also trivially secure by their definition.  These are both small, but important complaints.  But a larger complaint, and one that is much harder to see, is that that it is not clear that the NY formalism actually captures real world Bloom filters.

In particular, say that $\mathbf{B}_1$ is implementing a classic Bloom filter.  Then the hash functions $h_1,h_2,\ldots,h_k$ are either sampled from some implicit family~$\mathcal{H}$ by~$\mathbf{B}_1$ (recall that this algorithm is randomized), or they are hard-coded into the description of~$B_1$.  Let's assume the former, for the moment.  In order for~$B_2$ to be able to respond to set-membership queries, it must have $h_1,h_2,\ldots,h_k$ as well.  Since~$B_2$ receives only the representation~$M$ as input, it must be the case that $h_1,h_2,\ldots,h_k$ are encoded into~$M$ somehow.  But the text strongly suggests, in several places, that~$M$ does \emph{not} include these.  Both NY and classical analysis of Bloom filters speak of the number of bits used to represent the set~$\mathcal{S}$: the classical analysis means only the number of bits in the actual array, and NY make comparisons throughout between the number of bits~$m$ used by their instantiations and the classical bounds.  Morevover, the Bloom filter they construct in one of their main positive results clearly \emph{does not} count as part of the representation size the hash functions used to indicate array locations. Thus, if we assume that $\mathbf{B}_1$ is sampling $h_1,h_2,\ldots,h_k$, it seems that their formalization fails to capture the basic Bloom filter construction; at best, it is hard to see clearly that it does.

On the other hand, we can assume that the hash functions are implicitly hard-coded into~$\mathbf{B}_1$ (and $\mathbf{B}_2$).  Then we can treat~$\mathbf{B}_1$ as deterministic, since it will simply carry out the steps required to populate an array using these hash functions, and output the array~$M$ as the representation.  If we apply Kirchoff's rule, the descriptions of~$\mathbf{B}_1,\mathbf{B}_2$ are known to the adversary, who is also provided with~$\mathcal{S}$.  In this case, the adversary can compute~$M$ itself, as well as test for false-positives itself.  So it isn't clear how the security notion helps to reason about difficulty of finding a false-positive.  Moreover, NY stresses (at least once) that the representation is \emph{not} given to the adversary in their notions.  So it seems unlikely that they intended for $h_1,h_2,\ldots,h_k$ to be hard-coded into the algorithms.
